taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-01-07 paper/manuscript.Rmd

```{r}
td_create("gbif")
```

```{r}
url <- "ftp://ftpext.usgs.gov/pub/er/md/laurel/BBS/DataFiles/SpeciesList.txt"
col_names <- c("Seq", "AOU", "English_Common_Name", "French_Common_Name",
               "Spanish_Common_Name", "ORDER", "Family", "Genus", "Species")
bbs <- readr::read_table(url, 
                         skip = 9, 
                         col_names = col_names, 
                         col_types = "ccccccccc")

@@

```{r}
species_list = paste(bbs$Genus, bbs$Species)
length(species_list)
```

```{r}
bbs_ids <- 
data_frame(species = species_list) %>% 
  mutate(gbif = get_ids(species, "gbif", "prefix"),
         col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
         wikidata = get_ids(species, "wd", "prefix"))

>>>>

```{r}
td_create("all")
```

```{r}
bbs <- read_tsv(system.file("extdata/bbs.tsv", package="taxadb"))
```

```{r}
dim(bbs)
```

```{r}
bbs_ids <- 
bbs %>% select(species) %>%
  mutate(gbif = get_ids(species, "gbif", "prefix"),
          col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
     wikidata = get_ids(species, "wd", "prefix"),
          ott = get_ids(species, "ott","prefix") 
  )

@@

```{r}
bbs_ids <- bbs %>% 
  select(species) %>% 
  mutate(species = clean_names(species)) %>%
  mutate(gbif = get_ids(species, "gbif", "prefix"),
          col = get_ids(species, "col", "prefix"),
         itis = get_ids(species, "itis", "prefix"),
         ncbi = get_ids(species, "ncbi", "prefix"),
     wikidata = get_ids(species, "wd", "prefix"),
          ott = get_ids(species, "ott","prefix") 
  )

bbs_ids %>% 
  select(-species) %>% 
  purrr::map_dbl(function(x) sum(!is.na(x)))
```

```{r}
ids <- get_ids(clean_names(bbs$species), "ott", "prefix")
unmatched <- bbs$species[is.na(ids)]
clean_names(unmatched)
```

```{r}
unmatched <- bbs$species[is.na(bbs_ids$ott)]
length(unmatched)

drop_sp.(unmatched) %>%
  binomial_names()

clean_names(unmatched)
```

```{r}
bbs_ids %>% 
  select(-species) %>% 
  purrr::transpose() %>%
  purrr::map_dbl(function(x) sum(!is.na(x)) < 1) %>% sum()
```
